---
title: "Network of Foreign Policy Experts"
author: "Po-Sheng Lee"
date: "2019/3/8"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages attaching}

library(tidyverse)
library(statnet)
library(magrittr)
library(readxl)
library(sna)
library(igraph)
library(ggraph)
library(knitr)

```
# Question

## From Panda Huggers to Rivarly
- Why the foreign policy changes, especially the changes of US views towrad China

- The classical IR answer
    - Realism (Here comes Mearsheimer) 
    - Thucydides Trap by Graham Allison

## Why I am not a big fan of these answers
  
- The presumption of nation state as the only player

- The dynamics among policy makers is not captured by the theory
    - Why the changes of U.S happened in recent years? (why not five years ago?)
    - Why the changes are so fast and bipartisan?

# A network approach 

## What Network
- Foreign policy elites network constituted by
    - Academic, Journalists, Career Diplomat and Militaries

- Structure of Network matters
    - Duality of Network 
        - The organization network
        - The network of elites
    - Cliques and Structual Holes
        - Some elites' changes of mind can have tremendous fallout effect

## Empirical Strategies
- A sampling list from the authorship in <span style="color:blue">Foreign Affairs</span>
    - Search in title and abstract for *China*

- The biographical data from the internet
    - The employment history
        - Gov Employee, Gov Consultant
    - Institutions on elite has been stayed
        - Think Tank, University, Committees 
    - Exclude journalists

- Blockmodelling of the data

## Preliminary Research Questions

- What network do <span style="color:red"> Republican</span> and <span style="color:blue">Democrats</span> rely on?

# Data and Results
## Raw data

```{r raw data}
RawData <- read_excel("data/Expert Network Sociometric Dataset for analysis.xlsx", sheet = "network ")
RawData[is.na(RawData)] <- 0
kable(RawData)

```

```{r data manipulation}

sociometric_translation <- RawData %>%
  select(-c(Name, appointment_obama, appointment_bush,gov_consultant,gov_employee)) %>%
  as.matrix()

sociometric_elites <- sociometric_translation %*% t(sociometric_translation)
sociometric_institutions <- t(sociometric_translation) %*% sociometric_translation


sociometric_attributes <- RawData %>%
  select(c(Name, appointment_obama, appointment_bush,gov_consultant,gov_employee))
  
net_elite <- network(sociometric_elites, matrix_type = "adjacency", 
                     ignore.eval=FALSE,names.eval="membership")

net_institutions <- network(sociometric_institutions, matrix_type = "adjacency",
                            ignore.eval=FALSE,names.eval="membership")

```

## The network

```{r drawing network}

gplot(net_elite, vertex.col = 2, displaylabels = FALSE)
gplot(net_institutions, vertex.col = 2, displaylabels = FALSE)

```
## Slide with Plot

```{r pressure}
plot(pressure)
```

