---
title: "Network of Foreign Policy Experts"
author: "Po-Sheng Lee"
date: "2019/3/8"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages attaching}

library(tidyverse)
library(igraph)
library(ggraph)
library(statnet)
library(magrittr)
library(readxl)
library(sna)
library(intergraph)
library(knitr)
library(Zelig)

```
# Question

## From Panda Huggers to Rivarly
- Why the foreign policy changes, especially the changes of US views towrad China

- The classical IR answer
    - Realism (Here comes Mearsheimer) 
    - Thucydides Trap by Graham Allison

## Why I am not a big fan of these answers
  
- The presumption of nation state as the only player

- The dynamics among policy makers is not captured by the theory
    - Why the changes of U.S happened in recent years? (why not five years ago?)
    - Why the changes are so fast and bipartisan?

# A network approach 

## What Network
- Foreign policy elites network constituted by
    - Academic, Journalists, Career Diplomat and Militaries

- Structure of Network matters
    - Duality of Network 
        - The organization network
        - The network of elites
    - Cliques and Structual Holes
        - Some elites' changes of mind can have tremendous fallout effect

## Empirical Strategies
- A sampling list from the authorship in <span style="color:blue">Foreign Affairs</span>
    - Search in title and abstract for *China*

- The biographical data from the internet
    - The employment history
        - Gov Employee, Gov Consultant
    - Institutions on elite has been stayed
        - Think Tank, University, Committees 
    - Exclude journalists

## Preliminary Research Questions

- What network do <span style="color:red"> Republican</span> and <span style="color:blue">Democrats</span> rely on?

- On the elite network
    - Actors' prominance
        - centrality (could be a regression)
    - Group Effect
        - k-cores
        - community effect
    - Model
        - Block Model
        - ERGM ?


# Data and Results
## Raw data

```{r raw data}
RawData <- read_excel("data/Expert Network Sociometric Dataset for analysis.xlsx", sheet = "network ")
RawData[is.na(RawData)] <- 0
kable(RawData)

```

```{r data manipulation}

sociometric_translation <- RawData %>%
  select(-c(Name, appointment_obama, appointment_bush,gov_consultant,gov_employee)) %>%
  as.matrix()

sociometric_elites <- sociometric_translation %*% t(sociometric_translation)
sociometric_institutions <- t(sociometric_translation) %*% sociometric_translation


## The appointment data for visualization
sociometric_attributes <- RawData %>%
  select(c(Name, appointment_obama, appointment_bush,gov_consultant,gov_employee)) %>%
  add_column(memberships = diag(sociometric_elites)) %>%
  mutate(appointment = case_when(
    appointment_obama == 1 & appointment_bush == 1 ~ "both",
    appointment_obama == 0 & appointment_bush == 0 ~ "none",
    appointment_obama == 1 & appointment_bush == 0 ~ "obama",
    appointment_obama == 0 & appointment_bush == 1 ~ "bush"))
  
  
  
net_elite <- network(sociometric_elites, matrix.type = "adjacency", directed = FALSE,
                     ignore.eval=FALSE,names.eval="membership")

network::set.vertex.attribute(net_elite, "vertex.names", sociometric_attributes$Name)
network::set.vertex.attribute(net_elite, "appointment", sociometric_attributes$appointment)
network::set.vertex.attribute(net_elite, "gov_employee", sociometric_attributes$gov_employee)
network::set.vertex.attribute(net_elite, "gov_consultant", sociometric_attributes$gov_consultant)
network::set.vertex.attribute(net_elite, "memberships", sociometric_attributes$memberships)



net_institutions <- network(sociometric_institutions, matrix.type = "adjacency", directed = FALSE,
                            ignore.eval=FALSE,names.eval="interlock")

net_elite_igraph <- asIgraph(net_elite)
net_institutions_igraph <- asIgraph(net_institutions)

#clean the isolated one to draw the network
net_elite_igraph_clean <- delete_vertices(net_elite_igraph, which(igraph::degree(net_elite_igraph)==0))

```

## The network
```{r drawing elite network}

set.seed(1069) ## transparency
ggraph(net_elite_igraph_clean, layout = "lgl") +
  geom_edge_link(edge_alpha = 0.1) +
  geom_node_point(aes(color = appointment))


```

---


```{r drawing institution network}

set.seed(1069) ## transparency
ggraph(net_institutions_igraph, layout = "fr") +
  geom_edge_link(edge_alpha = 0.1) +
  geom_node_text(aes(label = vertex.names), size = 1.5, repel = TRUE)

```


## Summary of Network
```{r descriptive of network}

df_summary_network <- data.frame(
  size = c(network.size(net_elite), network.size(net_institutions)),
  density = c(gden(net_elite), gden(net_institutions)),
  diameter = c(diameter(net_elite_igraph), diameter(net_institutions_igraph)),
  clustering = c(transitivity(net_elite_igraph), transitivity(net_elite_igraph))
)

row.names(df_summary_network) <- c("Network of Elites", "Network of Institutions")

kable(df_summary_network)

```


## Centrality


```{r centrality of elite}

## create a dataframe for centrality, add name
df_centrality_elite <- data.frame(
  eigenvector = evcent(net_elite, gmode = "graph"),
  degree = degree(net_elite, gmode = "graph"), 
  betweenness = betweenness(net_elite, gmode = "graph"))
row.names(df_centrality_elite) <- net_elite %v% "vertex.names"

## store the centrality to the attribute data
sociometric_attributes %<>%
  left_join(rownames_to_column(df_centrality_elite, var = "Name"), by = "Name")
## order by eigenvector
df_centrality_elite <- df_centrality_elite[order(-df_centrality_elite$eigenvector),]
##bind the network data to the personal data
df_centrality_elite <- rbind(c(centralization(net_elite, evcent),
                               centralization(net_elite, degree),
                               centralization(net_elite, betweenness)),
                             df_centrality_elite)

row.names(df_centrality_elite)[1] <- "Network Centralization"
kable(df_centrality_elite)


```


---


```{r centrality and employment}

z_centrality_out1 <- zelig(appointment_obama ~ betweenness, model = "logit", 
                           data = sociometric_attributes,cite = FALSE)
z_centrality_out2 <- zelig(appointment_obama ~ eigenvector, model = "logit", 
                           data = sociometric_attributes,cite = FALSE)
z_centrality_out3 <- zelig(appointment_bush ~ betweenness, model = "logit", 
                           data = sociometric_attributes,cite = FALSE)
z_centrality_out4 <- zelig(appointment_bush ~ eigenvector, model = "logit", 
                           data = sociometric_attributes,cite = FALSE)

summary(z_centrality_out3, odds_ratio = TRUE)
```


---
```{r centrality of institution}

df_centrality_institutions <- data.frame(
  eigenvector = evcent(net_institutions, gmode = "graph"),
  degree = degree(net_institutions, gmode = "graph"), 
  betweenness = betweenness(net_institutions, gmode = "graph"))
row.names(df_centrality_institutions) <- net_institutions %v% "vertex.names"

df_centrality_institutions <- df_centrality_institutions[order(-df_centrality_institutions$eigenvector), ]

df_centrality_institutions <- rbind(c(centralization(net_elite, evcent),
                                      centralization(net_elite, degree),
                                      centralization(net_elite, betweenness)),
                                    df_centrality_institutions)

row.names(df_centrality_institutions)[1] <- "Network Centralization"
kable(df_centrality_institutions)

```

## Subgroup
```{r visualize subgroup}

```

## Block Model
```{r blockmodelling}

```


## Some Challenges

- Cannot ruleout the non-network effect (Data)
    - Include some other personal data
- Modelling Issues    
    - Still not clear whether the block model works or not
    - Specification of ERGM is not clear

## Looking Ahead

- Multiple networks 
    - academic citation, journalist
- The network in other countries

- Long term changes of network


